Supplementary Materials for ``An Efficient Forecasting Approach to Reduce Boundary Effects in Real-Time Time-Frequency Analysis''

### 2021-01-24 Paper/Supplementary material/SupMat.tex
figs

{\color{red}
\section{Application to a Multicomponent Cardiac Signal}
We consider a cardiac signal, namely an arterial blood pressure recording, sampled at $1000$~Hz. In addition to the blood pressure measurement, this signal contains a slow varying component, which is the respiratory component. Fig.~\ref{fig:abp} displays the ordinary and boundary-free SSTs of a 150-second-long extract of this signal, obtained via {\sf BoundEffRed}. This TF analysis brings out both components---the cardiac component, the most energetic, is located around the fundamental frequency $1$~Hz and its multiples, while the respiratory component, less visible, is located around $0.2$~Hz. The performance index of this representation takes the value $D=0.XXX$. Note that, here, boundary effects are only reduced on the right-side boundary of the TF domain. This means that {\sf BoundEffRed} has reduced the right-side boundary effects by about $XX\%$ with respect to the ordinary SST. This shows the ability of our algorithm to work on signals containing several nonstationary components.

\begin{figure}
\centering
%\includegraphics[width=.48\textwidth]{ABPsst.eps}
%\includegraphics[width=.48\textwidth]{ABPberSST.eps}
\caption{Ordinary SST (left) and boundary-free SST (right) of an arterial blood pressure recording}
\label{fig:abp}
\end{figure} 
}

>>>>

{\color{red}
\section{Application to a Multicomponent Cardiac Signal}
We consider a cardiac signal, namely an arterial blood pressure recording, sampled at $1000$~Hz. In addition to the blood pressure measurement, this signal contains a slow varying component, which is the respiratory component. Fig.~\ref{fig:abp} displays the ordinary and boundary-free SSTs of a 150-second-long extract of this signal, obtained via {\sf BoundEffRed}. This TF analysis brings out both components---the cardiac component, the most energetic, is located around the fundamental frequency $1$~Hz and its multiples, while the respiratory component, less visible, is located around $0.2$~Hz. The performance index of this representation takes the value $D=0.850$. Note that, here, boundary effects are only reduced on the right-side boundary of the TF domain. This means that {\sf BoundEffRed} has reduced the right-side boundary effects by about $15\%$ with respect to the ordinary SST. This shows the ability of our algorithm to work on signals containing several nonstationary components.

\begin{figure}
\centering
\includegraphics[width=.48\textwidth]{ABPsst.eps}
\includegraphics[width=.48\textwidth]{ABPberSST.eps}
\caption{Ordinary SST (left) and boundary-free SST (right) of an arterial blood pressure recording}
\label{fig:abp}
\end{figure} 
}
